Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-20 cosmic_voids.tex
Initial analysis of velocity profiles

>>>>

Additionally, in middle panels of Fig. \ref{fig:RhoVel} we calculate 
radial projected velocity profiles, where positive values implies outflow 
of matter, while negative ones indicates infall flows, all from the void 
centre.

A general feature of subcompensated voids is outward velocity profiles, 
indicating that matter all along these voids and their outsides is being 
pulled out. On the other hand, overcompensated voids exhibit initially
outward profiles, as expected from a low density region. However, 
approximately at the radius of the compensation ridge, the velocity becomes 
negative, thus indicating an infall flow of matter further than the 
compensation ridge. This shows that the high density structures associated 
to a compensation ridge indeed dominate the matter flow from inside the void 
as well as falling flows from outsides.
